Modern Graph Generators: A Survey

### 2018-11-25 data_sets.tex
Sherif Changes

Large scale graph analytics systems are usually benchmarked using a combination of
real-world and synthetically generated graphs. Because of the rapid evolution of such
systems and their increasing capability to process larger graphs, the datasets
typically used  in the literature quickly change overtime. The most commonly
used datasets (which can be downloaded from several graph dataset
repositories~\cite{snapnets,lawalgo}) are:
\begin{itemize}
  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
    researchers from DBLP are represented as vertices and there exists an edge
    between them if they have published a paper together.
  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
    network, such that each vertex represents a product, while edges between two products
    exists if a person bought both of them.
  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
    networks from the US.
  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
    represent the users and the edges the acquittances between them.
  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
    where vertices represent persons and the edges their friendships.
  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
    the follower-followee interaction of Twitter.
  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
    Orkut, where nodes represent persons and edges their relationships.
  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
    websites and edges represent the hyperlinks between them.
  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
    vertices represent websites and the edges represent the hyperlinks connecting them.
\end{itemize}

>>>>

Large scale graph analytics systems are usually benchmarked using a combination of
real-world and synthetically generated graphs. Because of the rapid evolution of such
systems and their increasing capability to process larger graphs, the datasets
typically used  in the literature quickly change overtime. The most commonly
used datasets (which can be downloaded from several graph dataset
repositories~\cite{snapnets,lawalgo}) are:
\begin{itemize}
  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
    researchers from DBLP are represented as vertices and there exists an edge
    between them if they have published a paper together.
  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
    network, such that each vertex represents a product, while edges between two products
    exists if a person bought both of them.
  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
    networks from the US.
  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
    represent the users and the edges the acquittances between them.
  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
    where vertices represent persons and the edges represent the friendship relationship between them.
  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
    the follower-followee interaction of Twitter.
  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
    Orkut, where nodes represent persons and edges their relationships.
  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
    websites and edges represent the hyperlinks between them.
  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
    vertices represent websites and the edges represent the hyperlinks connecting them.
\end{itemize}

### 2018-11-25 generators_community_detection.tex
Sherif Changes

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of different sizes and
densities. The generator generates communities of different sizes following a
power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which consists of the fraction of
edges in the graph connecting nodes that belong to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process starts with an empty graph and incrementally fills in the
adjacency matrix by obeying the described constraints.

>>>>

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of different sizes and
densities. The generator generates communities of various sizes following a
power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which consists of the fraction of
edges in the graph connecting nodes that belong to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process starts with an empty graph and incrementally fills in the
adjacency matrix by considering the described constraints.
